Synthesising and Verifying Closed-loop Digital Control Systems

### 2016-09-21 paper/paper.tex
+ general structure of the sec on program synthesis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example}

@@

We use CounterExample-Guided Inductive Synthesis (CEGIS), as
illustrated in Fig~\ref{fig:CEGIS}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Example} \label{sec:running-ex}

@@

% We use CounterExample-Guided Inductive Synthesis (CEGIS), as
% illustrated in Fig~\ref{fig:CEGIS}.

In order to synthesise closed-loop digital control systems, we use a
program synthesis engine.  Nowadays, such engines are used
increasingly often in program verification
\cite{DBLP:conf/cav/0001A14,DBLP:conf/lpar/DavidKL15}.  Our program
synthesiser makes use of Counter-Example Guided Inductive Synthesis
(CEGIS) \cite{sketch}.  We start by presenting its general
architecture followed by describing the parts specific to control
systems.

%specialised it for stream refactoring.  
% adding JST for stream refactoring

\paragraph{General architecture of the program synthesiser}
%
The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}.

\paragraph{Elements specific to control systems}

\paragraph{Running example synthesis}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
Our goal is to synthesise ...
\cdsay{Finish this once the example is working.}
